%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size
\input{structure.tex} % Include the file specifying document layout
\usepackage{xeCJK}
\usepackage{enumitem}
\setCJKmainfont{STSong}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%    NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Chong Guo} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address:} \> 215-5155 Watling at Burnaby BC \\[2mm] % Address
{\bf Github:} \> \href{https://www.github.com/Armour}{https://www.github.com/Armour} \\ % Github
\end{tabbing}
\vspace{-3mm}
}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Phone:} \> +0 778-681-8660 \\[2mm] % Mobile phone
{\bf Email:} \> \href{mailto:gc497052684@gmail.com}{gc497052684@gmail.com} \\ % Email address
\end{tabbing}
\vspace{-3mm}
}
\rule{\textwidth}{0.5mm}\\ % Rule under the header

%------------------------------------------------

\fontdimen2\font=1.5\fontdimen2\font

%------------------------------------------------

\vspace{6mm}
November 1, 2015

\vspace{4mm}

Jami Dayton

HR Peep

East Side Games Studio

\#200-116 West Hastings Street

Vancouver, BC V6B 1G8

\vspace{4mm}

RE: Coop Programmer

\vspace{4mm}

Dear Ms. Dayton,

\vspace{4mm}

I am writing to express my interest in the Coop Programmer position that is available at East Side Games Studio as advertised on Simon Fraser University Co-op website. East Side Games is a independent and multicultural studio working on cross-platform game development with creative inspiration and purpose-built technologies, as a Computer Science student with strong interests and past experiences in both iOS and game development, I believe my abilities could be perfectly applied to this position. I think the opportunity to collaborate with such a talented, highly-motivated team would be invaluable for me.

\vspace{4mm}

As a Computer Science student, and someone who is extremely passionate about every interesting and useful computer technologies, I have participated in different kinds of projects including web, app, database and game development, through which I have learned many useful programming languages like Node.js, Objective-C, SQL(PostgreSQL) and C++. For example, in one of my iOS project, ``云格子铺'', which is used for second-hand trades among a bunch of schools, I first listened to lectures about UI design and Obejective-C on Coursera for about two weeks, then designed and implemented it with one of my friends in several months, during which time I learned how to use Core Data, Auto Layout, UI Animation and various third-party open source libraries, we collaborated through Git and still maintaining it now. By getting involved in this project, cooperated with teammate and keeping learning new things with enthusiasm, I improved my soft kills such as efficient communication, working under pressure and in a timely manner. Other projects are also benefited me a lot, like using PHP or Node.js as back-end to develop website, integrating skyline queries on incomplete data into PostgreSQL database and writing RPG game using C++ with Qt and Boost libraries.

\vspace{4mm}

Apart from those projects, in school I am also performed well. I got \$5,000 Entrance Award and always accomplish assigned tasks with chariness and responsibility in each course like operating system, networking and data structure. Due to my quick mind, clear though and standout coding skills in solving some data structure problems, I was selected for the 2015 ACM-ICPC Asia Amritapuri Regional Contest which will be host on November 14th, wish I can redound to the good name of the whole school. Additionally, I started to learn Minecraft modding in recent times, which is really a fascinating topic I think. You can find the source codes of almost all the projects that mentioned above and in my resume in my Github.

\vspace{4mm}

By having great interests in iOS and game development and being involved in multiple projects, I believe I am an perfect match for this position. Thank you for your time reviewing my resume. I welcome the opportunity to discuss in a personal interview about my qualifications and fit for the position. Feel free to reach me at armourg@sfu.ca at your earliest convenience.

\vspace{4mm}

Sincerely,

\vspace{12mm}

Chong Guo

%------------------------------------------------

\end{document}