%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size
\input{structure.tex} % Include the file specifying document layout
\usepackage{xeCJK}
\usepackage{enumitem}
\setCJKmainfont{STSong}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%    NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Chong Guo} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address:} \> 215-5155 Watling at Burnaby BC \\[2mm] % Address
{\bf Github:} \> \href{https://www.github.com/Armour}{https://www.github.com/Armour} \\ % Github
\end{tabbing}
\vspace{-3mm}
}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Phone:} \> +0 778-681-8660 \\[2mm] % Mobile phone
{\bf Email:} \> \href{mailto:gc497052684@gmail.com}{gc497052684@gmail.com} \\ % Email address
\end{tabbing}
\vspace{-3mm}
}
\rule{\textwidth}{0.5mm}\\ % Rule under the header
\vspace{-2mm}

%----------------------------------------------------------------------------------------
%    TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNICAL SKILLS}
\vspace{-2mm}
\skillgroup{Languages}{C/C++, \ Objective-C, \ Node.js, \ Python, \ PHP, \ Java, \ JavaScript, \ HTML5, \ Verilog}
\skillgroup{Editors}{Vim, \ Emacs, \ Atom, \ Sublime Text}
\skillgroup{Operating Systems}{Mac OSX, \ Linux (Ubuntu, CentOS, Debian), \ Windows, \ iOS}
\skillgroup{Database}{PostgreSQL, \ MySQL, \ SQL Server, \ MongoDB, \ Redis}
\skillgroup{Miscellaneous} {Git, \ OpenCV, \ Qt, \ MatLab, \ PostgreSQL Server Programming, \ Minecraft modding, \ \LaTeX}

%----------------------------------------------------------------------------------------
%    TRANSFERABLE SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TRANSFERABLE SKILLS}
\begin{itemize}
	\item Able to work under pressure and in time sensitive situation
	\item Excellent learning and problem solving skills
	\item Work well with teammates and sometimes have creative inspiration
	\item Multi-cultural with Mandarin as mother tongue and can understand some Japanese
\end{itemize}

%----------------------------------------------------------------------------------------
%    WORK EXPERIENCES SECTION
%----------------------------------------------------------------------------------------

\section{WORK EXPERIENCES}
\vspace{-2mm}
\parbox{0.5\textwidth}{ % iOS 
\begin{tabbing}
\hspace{4mm} \= \kill
\>\textbf{\ \ iOS Developer(Part-Time), ZaoFeng E-commerce Ltd} \textit{(Zhejiang, China)}
\end{tabbing}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
Apr. 2015 - Present
\end{tabbing}
}
\vspace{-3mm}
\begin{itemize}[leftmargin=16mm]        
        \item Designed, implemented and maintaining an iOS App ``云格子铺'' which is used for second-hand trades among thousands of students in Zhejiang Province.
        \item Cooperated with another developer using Git (in company's Gitlab) to provide a good collaborative environments.
        \item Responsible for bandwidth, memory and performance optimisation to reduce total data costs.
        \item Already Put this app on Apple Appstore in China and received 4+ stars rating.
\end{itemize}

\vspace{-1mm}
\parbox{0.5\textwidth}{ % 8BTCX
\begin{tabbing}
\hspace{4mm} \= \kill
\>\textbf{\ \ Back-End Developer(Contract), ShiChuo Technologies Ltd} \textit{(Zhejiang, China)}
\end{tabbing}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
July - Sept. 2014
\end{tabbing}
}
\vspace{-3mm}
\begin{itemize}[leftmargin=16mm]
		\item Constructed a information sharing website `8btcx' which has been used among several companies.
		\item Assisted in designing and development of website according to design specifications.
		\item Developed back-end using Linux, Apache, MySQL, and PHP(with Codeigniter framework) and maintained it in a 24/7 environment.
		\item Normalized database tables and performed extensive query optimization to boost website performance.
        \item Demo can be found in \textit{\underline{http://www.armourcy.com/8btcx}}
\end{itemize}


%----------------------------------------------------------------------------------------
%    PROJECT EXPERIENCES SECTION
%----------------------------------------------------------------------------------------

\section{Project Experiences}

% PostgreSQL
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{4mm} \= \kill
\>\textbf{\ \ PostgreSQL Database Extension} \textit{(Data Mining Lab, Zhejiang University)}
\end{tabbing}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
May - Sept. 2015
\end{tabbing}
}
\vspace{-3mm}
\begin{itemize}[leftmargin=16mm]
        \item Implemented k-skyband, constrained skyline and group-by skyline queries using pl/pgSQL and C to make skyline query on incomplete data more efficient.
        \item Learned PostgreSQL server side programming and successfully integrated three queries into PostgreSQL system.
        \item Performed quality testing and assurance for those three queries to meet users needs.
\end{itemize}

% APRS
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{4mm} \= \kill
\>\textbf{\ \ APRS Project} \textit{(Project Training Course, Zhejiang University)}
\end{tabbing}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
Mar - July 2015
\end{tabbing}
}
\vspace{-3mm}
\begin{itemize}[leftmargin=16mm]
        \item Worked as the group leader of Operations Engineers with passion and responsibility.
        \item Maintained the server, built Gitlab and some other webpages like wiki for everyone.
        \item Programmed both front-end and back-end, helped integrate each group's code together.
        \item Gave presentations about the whole project's completeness each week to ensure tasks going well.
\end{itemize}

% Object Detection
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{4mm} \= \kill
\>\textbf{\ \ Object Detection Project} \textit{(Dormitory, Zhejiang University)}
\end{tabbing}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
July 2014 - Sept. 2014
\end{tabbing}
}
\vspace{-3mm}
\begin{itemize}[leftmargin=16mm]
        \item Implemented object detection using C++ and OpenCV to provide competitive object detection rates in real-time.
        \item Self-learned Machine Learning Course on Coursera on time.
        \item Summarized and programmed many algorithms like Liner Regression, Neural Network, SVM, etc.
\end{itemize}

% Magic Tower
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{4mm} \= \kill
\>\textbf{\ \ Magic Tower Game} \textit{(Object-Oriented Programming Course, Zhejiang University)}
\end{tabbing}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
Nov. 2014 - Jan. 2015
\end{tabbing}
}
\vspace{-3mm}
\begin{itemize}[leftmargin=16mm]
        \item Implemented an RPG game using Qt and C++ which is about a warrior saving the princess who has been trapped in the top of the tower. \ \textit{(Code : \underline{https://github.com/Armour/Magic-Tower-Qt)}}
        \item Connected with remote database (MYSQL) using data orientated structure which allows fast computation.
        \item Gave different ends according to player's choice, added NPC, event and even cheating function to maximize players' gaming experiences. 

\end{itemize}

% Object Detection
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{4mm} \= \kill
\>\textbf{\ \ Military Training Webpage} \textit{(QSC Tech Organization, Zhejiang University)}
\end{tabbing}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
July - Sept. 2014
\end{tabbing}
}
\vspace{-3mm}
\begin{itemize}[leftmargin=16mm]
        \item Implemented the Military Training Webpage which is used by every freshman in ZJU using PHP.
        \item Maintained 24/7 high volume availability demands until our school's military education and training end.
        \item Demo can be found in \textit{\underline{http://www.armourcy.com/military-training}}
        \item Admin panel demo in \textit{\underline{http://www.armourcy.com/military-training/admin}} (Username:test \  Password:test)
\end{itemize}

%----------------------------------------------------------------------------------------
%    EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\vspace{-3mm}
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{4mm} \= \kill
\>\textbf{\ \ Simon Fraser University, Vancouver, Canada}\\[2mm]
\hspace{13mm} Computer Science - Bachelor's Degree
\end{tabbing}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
Sept. 2015 - Present\\[2mm]
\end{tabbing}
}

\vspace{-3mm}
\parbox{0.5\textwidth}{
\begin{tabbing}
\hspace{4mm} \= \kill
\>\textbf{\ \ Zhejiang University, Hangzhou, China}\\[2mm]
\hspace{13mm} Computer Science - Bachelor's Degree \textit{(GPA: 4.15/5.00)}
\end{tabbing}
}
\hfill
\parbox{0.5\textwidth}{
\begin{tabbing}
Sept. 2013 - July 2015\\[2mm]
\end{tabbing}
}

%----------------------------------------------------------------------------------------
%    Awards SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\begin{itemize}[leftmargin=10mm]
    \item Simon Fraser University Entrance Award (\$5,000) \hfill 2015
    \item First Prize in NOIP (National Olympiad in Informatics in Provinces, China) \hfill 2011
\end{itemize}

%----------------------------------------------------------------------------------------
%    INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\begin{itemize}[leftmargin=10mm]
\begin{minipage}{0.5\linewidth}
    \item Freestyle inline skating
    \item Music/Bass
\end{minipage}
\begin{minipage}{0.5\linewidth}
    \item Video Games
    \item Travel
\end{minipage}
\end{itemize}

\end{document}
